### 2018-03-08 paper/sexSelectionSpacing-ver1.tex
Discuss no education duration and sex ratio results

% [How to read tables]
Tables \ref{tab:median_sex_ratio_low}, \ref{tab:median_sex_ratio_med}, and
\ref{tab:median_sex_ratio_high}
show predicted median duration and sex ratios by period, spell, and sex 
composition for the three different education levels separated by area of residence. 
The predictions are based on the estimation method described in 
Section \ref{sec:strategy}.
The standard errors for both measures are based on bootstrapping, where the 
original sample is resampled with replacement and the method is applied to 
the new sample.

@@

The cleanest test is comparing durations after only boys with durations after
only girls.
However, because of falling fertility the number of births to women with 
only sons becomes small in the later periods, especially for the third and 
fourth spell.
Hence, it is possible to have substantial differences in spacing that are
not statistically significant because of low power.
Furthermore, it is, in principle, possible to estimate the model taking 
into account the ordering of children.
This would, however, further lower the power of the test, by leading to 
one extra group for the third spell and four extra groups for the fourth spell.

@@

Each cell's predicted precent boys is tested against the natural percentage 
boys using the bootstrapped standard errors.
The natural sex ratio is approximately 105 boys to 100 girls or
51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
It is possible for the predicted percentage boys to be different from 
the natural rate either because of natural variation, any remaining
recall error, or sex selection.

% Median duration and sex ratio tables
\input{../tables/bootstrap_duration_sex_ratio_low.tex}

Table \ref{tab:median_sex_ratio_low} shows the predictions for women 
with no education.
Overall, spacing is shorter the fewer boys a couple has, but the
differences in median duration are never more than 3 months and most
are only one or two months
(the exceptions to this pattern are mostly for small cells).
Furthermore, although the median duration generally increases over 
time---with the exception of the first spell---there is little 
change in the relative pattern of durations across sex compositions
over time.
These results point to an absence of sex-selective abortions for 
this group of women, which is supported by predicted sex ratios
that mostly close to the natural sex ratio.%
\footnote{
I return to whether there are statistically significant 
differences below when examining sex ratios within spells.
}

@@

>>>>

% [How to read tables]
Tables \ref{tab:median_sex_ratio_low}, \ref{tab:median_sex_ratio_med}, and
\ref{tab:median_sex_ratio_high}
show predicted median duration and sex ratios by period, spell, and sex 
composition for the three different education levels separated by area of residence.%
\footnote{
Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
\ref{tab:p25_p75_low} show 25th and 75th percentiles durations.
} 
The predictions are based on the estimation method described in 
Section \ref{sec:strategy}.
The standard errors for both measures are based on bootstrapping, where the 
original sample is resampled with replacement and the method is applied to 
the new sample.

@@

The cleanest test is comparing durations after only boys with durations after
only girls, but the number of births to women with only sons becomes small 
in the later periods because of falling fertility.
Hence, it is possible to have substantial differences in spacing that are
not statistically significant because of low power, especially for the third 
and fourth spell.
It is, in principle, possible to estimate the model taking into account the 
ordering of children, but this would further lower the power of the test, by 
adding one extra group for the third spell and four extra groups for the fourth spell.

@@

Each predicted precent boys is tested against the natural percentage 
boys using the bootstrapped standard errors.
The natural sex ratio is approximately 105 boys to 100 girls or
51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
The predicted percentage boys may differ from the natural rate because of 
natural variation, any remaining recall error not corrected for, or 
sex selection.

\input{../tables/bootstrap_duration_sex_ratio_low.tex}

Women with no education follow a pattern consistent with son
preference with shorter spacing when they have only girls compared 
to when they have one or more sons, and the differences are often statistically 
significant as shown in Table \ref{tab:median_sex_ratio_low}.
Most of the women without education live in rural areas,
while there are relatively few urban women with no education.
There are especially very few urban women to based the third
and fourth spell results on, and I therefore focus on rural women.

Predicted median duration has generally increased over time within
each sex composition.
The exception is for the first spell, where there is little
change, and possibly even a small decline.
This decline may be the result of a combination of lower recall
error, increasing age at marriage, and better health.

The differences in duration across sex compositions are more 
pronounced with higher-order spells.
For the second spell, the difference in median duration between
having a girl or a boy as the first-born are mostly between 0.5 and 1 
month, although it varies from a low of 0.2 months for rural women 
in 1995--2004 period to a high of 1.5 months
for urban women in the 1985--1994 period.
Focusing on rural women for the third spell, the difference is,
on average, slightly over 1 months between only girls and only boys 
and the differences are statistically significant in all periods.
For rural women the differences for the fourth spell are just below
2 months, with the exception of the 1972--1984 period, which is
also the only period where the difference is not statistically significant.

It is possible that remaining recall error is behind some of the
smaller differences in duration.
One example is the second spell in the 1995--2004 period, where there 
are only 0.2 months difference between duration after one girl and 
duration after one boy.
Similarly, the small difference for the fourth spell in the 1972--1984
period may be the result of recall error with a very high 
percentage boys for women with three girls, despite no availability
of sex selection.

There are no clear time trends in the differences in median duration
across sex compositions or the predicted sex ratios across the four periods.
Despite some sex ratios that are statistically significantly higher 
than the natural sex ratio there is therefore little consistent evidence 
for the use of sex selection for women without education.
There has, for example, been relatively little change in the length
of spacing for rural women with two girls in the third spell and 
the predicted sex ratio was higher in the 1985--1994 period
than in the 2005--2016 period.
The possible exception is the fourth spell, where both duration 
and sex ratio has increased for women with three girls, although
the \emph{difference} across sex compositions has remained almost
the same.

@@

\subsection{Additional Duration Results}

\input{../tables/bootstrap_duration_p25_p75_low.tex}

\input{../tables/bootstrap_duration_p25_p75_med.tex}

\input{../tables/bootstrap_duration_p25_p75_high.tex}
